\LARGE \bf On the Commissioning of the 12 GeV HMS Drift Chambers, Electronics/Computer Dead Time Monitoring and Overview of the D(e,e'p)n Experimental Run Plan

### 2017-10-26 NRF_Final_Report/report.tex
started adding edtm section

Once all planes of the chamber were verified to have full occupancy, a High Voltage and threshold\footnote{The threshold set on the chamber is used to filter cosmic signals from noise by requiring that
the signals to be a certain size before discriminating them as logic signals, which are read out by the electronic modules.} scan was done to determine the plateau region. A high voltage scan was done first

@@

\section{MATH}

>>>>

Once all planes of the chamber were verified to have full occupancy, a High Voltage and threshold\footnote{The threshold set on the chamber is used to filter cosmic signals from noise by requiring 
the signal amplitude to cross a threshold before discriminating them to produce logic signals, which are read out by the electronic modules.} scan was done to determine the plateau region. A high voltage scan was done first

@@

\section{Electronic and Computer Deadtime Studies}
The procedure to determine the computer and electronic dead times is currently in the development stage in Hall C. The general idea is to use a pulse generator to produce
a fixed frequency pulse and feed it as early as possible into the electronic modules being used in the experimental setup. This pulse will interfere wth the actual signals
produced by physics, but its rate can be set orders of magnitude smaller such that its interference will be minimal and will have insignificant contribution to the deadtime.
By counting the number of pulses generated before sending them to the electronics chain, compared to the number of pulses that actually make it to the end of the chain and
are accepted by the TI (Trigger Interface) module, one may determine the dead time as follows:
\begin{equation}
  \text{dead time} = 1 - \frac{\# \text{ of accepted pulses}}{\# \text{ of generated pulses}}
\end{equation}
This is the total deadtime from the electronics and computer (TI module) that arises due to the finite processing time of the modules. The computer live time alone is calculated by the TI module since it has an
internal scaler which counts the number of input and output signals, and takes the ratio to determine the computer live time. This calculation can also be done externally as a cross-check by counting the number of signals that make it to the
TI via a scaler module, and comparing it to the number of accepted signals which is outputted by the TI and determined during the data analysis stage. The electronics deadtime is investigated by keeping the computer live time near 100$\%$ and
increasing the pulse generator rate to probe the rate limits of the electronics modules. One might argue that such high rates can reduce the computer live time itself which is true, however, such high rates can be pre-scaled by the TI by orders
of magnitude, such that the computer live time is preserved. For example, for every 10,000 counts/sec., (10 KHz), the TI counts 100 Hz., so that the rate is pre-scaled by a factor of 10$^{3}$. Using this technique, one can investigate the
effects of high rates on the electronic modules. In this limitng case, the total live time measured will be the electronics live time, since the computer live time will be fixed. \\
\indent The electronic and computer live time measurements have not been completed as there had been some issues encountered with the TI module that is currently being investgated by DAQ experts. These issues were uncovered during the
initial stages of the deadtime studies in which a pulse generator at various rates was used to probe the limits of the modules.
